### 2024-08-28 paper.tex
read up to lemma 6.7

        \par CONTINUE HERE.
        Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).

@@

        So, we just need to show that \(e_{i_kj}\)
        For \(i \in I\), we do it inductively.
        Fix \(i \in I\), and suppose we have already shown that for all \(i' \in I\) with \(q_{i'} > q_i\), we have \(\langle e_{ij} \rangle_{j \textrm{ arbitrary}} \subseteq W\).
        We will show that \(\langle e_{ij} \rangle_{j \textrm{ arbitrary}} \subseteq W\).
        \par To see this, we consider the chain beginning with \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i)\).
        (Recall \(v_i = A^{n - q_i} f_n - \sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i}\).)
        Because \(AW \subseteq W\), and \(b_{i,p_i} \neq 0\) (by definition of \(p_i\)), it suffices to show that \(\sum_{l = 1}^{p_i} b_{il} e_{i,k + q_i} \in W\).
        As explained in the proof of (1), we have \(A^{q_i + P_i} v_i \in \langle e_{lj} \rangle_{q_l \geq q_i}\).
        And since \(A^{q_i + P_i} v_i\) has row \(i\) zeroed out, in fact \(A^{q_i + P_i} v_i \in \langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i}\).

@@

        By our inductive hypothesis, \(\langle e_{lj} \rangle_{l : l \neq i \land q_l \geq q_i} \subseteq W\), and consequently \(A^{q_i + P_i} v_i \rightshift q_i + P_i \in W\).
        Since we know \(v_i - (A^{q_i + P_i} v_i \rightshift q_i + P_i) \in W\), this implies that \(v_i \in W\).
        Because \(A^{n - q_i} f_n \in W\), this then implies that \(\sum_{l = 1}^{p_i} b_{il} e_{i,l + q_i} \in W\), as desired.

@@

Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the previous lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
\par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
We are interested in this thing because the dimension of \(X_\mu\) is \(\gamma([\mu_1, ..., \mu_l])\).

\begin{lemma}
    \[\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    Now we consider how to get from \(L'\) to \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(L\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        \left[\sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k}))\right] & + \\
        \left[\sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} p_{i_k}\right] & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_k}\}} p_{i_k} & + \\
        \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1} + p_{i_k}} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
    \end{align*}    
\end{proof}

@@

\section{Linear Algebra Facts}
In this section we prove linear algebra facts that were used in the paper.
They are confined to this section to avoid interrupting the flow of the paper.

>>>>

        \par Now we are left with showing that \(\langle e_{ij} \rangle_{i,j : q_i < n} \subseteq W\).
        It suffices to show that \(e_{i, \lambda_i} \in W\) for each \(i\) with \(q_i < n\).

@@

        So, we just need to show that \(e_{i_k\lambda_{i_k}} \in W\) for each \(k \in \{1, ..., r\}\).
        We do this inductively; fix \(k\), and suppose we have already shown that \(e_{i_{k'}, \lambda_{i_{k'}}} \in W\) for \(k' < k\).
        We will show that \(e_{i_k, \lambda_{i_k}} \in W\).
        \par To see this, consider the chain beginning with \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}})\).
        (Recall \(v_{i_k} = A^{n - q_{i_k}} f_n - \sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}}\).)
        Since \(b_{i_k,p_{i_k}} \neq 0\) (by definition of \(p_{i_k}\)), it suffices to show that \(\sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}} \in W\).
        As explained in the proof of (1), we have \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \in \langle e_{lj} \rangle_{q_l \geq q_{i_k}}\).
        And since \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k}\) has row \(i_k\) zeroed out, in fact \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \in \langle e_{lj} \rangle_{l : l \neq i_k \land q_l \geq q_{i_k}}\).

@@

        By our inductive hypothesis, \(\langle e_{lj} \rangle_{l : l \neq i_k \land q_l \geq q_{i_k}} \subseteq W\), and consequently \(A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}} \in W\).
        Since we know \(v_{i_k} - (A^{q_{i_k} + p_{i_{k + 1}}} v_{i_k} \rightshift q_{i_k} + p_{i_{k + 1}}) \in W\), this implies that \(v_{i_k} \in W\).
        Because \(A^{n - q_{i_k}} f_n \in W\), this then implies that \(\sum_{l = 1}^{p_{i_k}} b_{i_kl} e_{i_k,l + q_{i_k}} \in W\), as desired.

@@

Let \(\mu(I, (\rho_i))\) be the shape of the Jordan basis given in the lemma.
Let \(X_\mu\) be the Springer fiber at \(J(\mu)\), and let \((X_{\mu, \alpha})_{\alpha \in \mathrm{SYT}(\mu)}\) be the irreducible components.
\par Given a zero-indexed list \(L = [L_0, ..., L_{l - 1}]\), we define \(\gamma(L) = \sum_i i L_i\).
We are interested in this thing because for any \(\alpha\), the dimension of \(X_{\mu, \alpha}\) is \(\gamma([\mu_1, ..., \mu_{k + 1}])\).

\begin{lemma}
    \[\gamma([\mu_1, ..., \mu_{k + 1}]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    Now we consider how to get from \(L'\) to \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(L\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        \left[\sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k}))\right] & + \\
        \left[\sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} p_{i_k}\right] & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_k}\}} p_{i_k} & + \\
        \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1} + p_{i_k}} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
    \end{align*}    
\end{proof}

@@

\section{Linear Algebra Facts}
In this section we prove linear algebra facts that were used earlier.
They are confined to this section to avoid interrupting the flow of the paper.
